Product plots

### 2011-06-27 prodplots-infovis.tex
'hand-holding' examples

Figure~\ref{fig:2d-table} shows three ways to represent the the 2d table of proportions of sex and happiness. The top table displays the {\bf joint distribution}, and allows us to answer questions of the form ``what proportion of all people are male and very happy?'' The middle two tables displays two {\bf conditional distributions}: the distribution of sex given happiness, and happiness given sex. These correspond to restricting the row or column sums to one, and support questions such as ``what proportion of pretty happy people are female?'' or ``what proportion of males are not too happy?''. Finally, the last table displays the two {\bf marginal distributions} of sex and happiness. These allow us to answer questions like ``what proportion of respondents were male'' or ``what proportion of respondents were very happy?''.

@@

  \begin{tabular*}{0.48\linewidth}{rrr}
\multicolumn{3}{l}{$f(happy| sex)$}\\
  \toprule
  & male & female \\
  \midrule
  not too happy & 0.43 & 0.57 \\
  pretty happy & 0.45 & 0.55 \\ 
  very happy & 0.43 & 0.57 \\
  \bottomrule
  \end{tabular*}
%
\hspace{1em}
  \begin{tabular*}{0.48\linewidth}{rrr}
\multicolumn{3}{l}{ $f(sex|happy)$, see fig. \ref{fig:fact-simple} (middle) }\\
  \toprule
  & male & female \\ 
  \midrule
  not too happy & 0.12 & 0.12 \\ 
  pretty happy & 0.57 & 0.55 \\ 
  very happy & 0.31 & 0.32 \\
  \bottomrule
  \end{tabular*}
  \\[1em]

>>>>

Figure~\ref{fig:2d-table} shows three ways to represent the the 2d table of proportions of sex and happiness. The top table displays the {\bf joint distribution}, and allows us to answer questions of the form ``what proportion of all people are male and very happy?'' -- the bottom left number tells us that these are 0.14. The middle two tables displays two {\bf conditional distributions}: the distribution of sex given happiness, and happiness given sex. These correspond to restricting the row or column sums to one, and support questions such as ``what proportion of pretty happy people are female?'' --  the table tells us that it's 0.55, or ``what proportion of males are not too happy?'' -- the top left number in the table tells us that that's 0.12. Finally, the last table displays the two {\bf marginal distributions} of sex and happiness. These allow us to answer questions like ``what proportion of respondents were male'' (0.44) or ``what proportion of respondents were very happy?'' (0.30).

@@

  \begin{tabular*}{0.49\linewidth}{rrr}
\multicolumn{3}{l}{$f(sex|happy)$, see fig. \ref{fig:fact-simple} (middle) }\\
  \toprule
  & male & female \\
  \midrule
  not too happy & 0.43 & 0.57 \\
  pretty happy & 0.45 & 0.55 \\ 
  very happy & 0.43 & 0.57 \\
  \bottomrule
  \end{tabular*}
%
\hspace{1em}
  \begin{tabular*}{0.47\linewidth}{rrr}
\multicolumn{3}{l}{$f(happy| sex)$}\\
  \toprule
  & male & female \\ 
  \midrule
  not too happy & 0.12 & 0.12 \\ 
  pretty happy & 0.57 & 0.55 \\ 
  very happy & 0.31 & 0.32 \\
  \bottomrule
  \end{tabular*}
  \\[1em]
